Algebraische Geometrie

### 2015-05-19 Algebraische Geometrie/AlgebraischeGeometrie.tex
Fehler fixen

\paragraph{Definition 5.24.}\label{5.24} Sei $S$ ein graduierter Ring, $X=\operatorname{Proj}(S)$ und $\mathcal{F}$ ein $\mathcal{O}_X$"~Modul. Der zu $\mathcal{F}$ \textit{assoziierte graduierte $S$"~Modul}\index{Modul!assoziiert} $\Gamma_\ast(\mathcal{F})$ ist definiert als die Gruppe
\[\Gamma_\ast(\mathcal{F})=\bigoplus_{n\in\mathbb{Z}}\Gamma(X,\mathcal{F}(n)) \]
mit der folgenden $S$"~Wirkung: Für $s\in S_d\cong\Gamma(X,\mathcal{O}_X(d))$ und $t\in\Gamma(X,\mathcal{F}(n))$ setze $st= s\otimes t\in\Gamma(X,\mathcal{F}(n)\otimes_{\mathcal{O}_X}\mathcal{O}_X(d))=\Gamma(X,\mathcal{F}(n+d))$.

>>>>

\paragraph{Definition 5.24.}\label{5.24} Sei $S$ ein graduierter Ring, $X=\operatorname{Proj}(S)$ und $\mathcal{F}$ ein $\mathcal{O}_X$"~Modul. Der zu $\mathcal{F}$ \textit{assoziierte graduierte $S$"~Modul}\index{Modul!assoziiert} $\Gamma_\ast(\mathcal{F})$ ist definiert als die Gruppe
\[\Gamma_\ast(\mathcal{F})=\bigoplus_{n\in\mathbb{Z}}\Gamma(X,\mathcal{F}(n)) \]
mit der folgenden $S$"~Wirkung: Ein $s\in S_d$ induziert ein $s\in \Gamma(X,\mathcal{O}_X(d))$. Für $t\in\Gamma(X,\mathcal{F}(n))$ setze $st= s\otimes t\in\Gamma(X,\mathcal{F}(n)\otimes_{\mathcal{O}_X}\mathcal{O}_X(d))=\Gamma(X,\mathcal{F}(n+d))$.
